---
title: "Homework 1"
author: Tianheng Hu
output: github_document
---

This is my solution to HW1

```{r libraries}
library(tidyverse)
#install.packages("palmerpenguins")
library(palmerpenguins)
```


## Problem 1
Create a data frame with the specified elements

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
)

```


Take the mean of each variable in my data frame.

```{r mean_pull}
mean(pull(prob1_df,samp))
mean(pull(prob1_df,samp_gt_0))
mean(pull(prob1_df,char_vec))
mean(pull(prob1_df,factor_vec))
```

I can take the means of numeric and logic but not of character and factor.


```{r try_numeric}
as.numeric(pull(prob1_df,samp))
as.numeric(pull(prob1_df,samp_gt_0))
as.numeric(pull(prob1_df,char_vec))
as.numeric(pull(prob1_df,factor_vec))
```

I can change numeric, logic and factor to numeric but not character. 
We can't take means of a type of data that cannot be converted to numeric.

```{r change_type_multiply}
as.numeric(pull(prob1_df,samp_gt_0)) * pull(prob1_df,samp)
as.factor(pull(prob1_df,samp_gt_0)) * pull(prob1_df,samp)
as.numeric(as.factor(pull(prob1_df,samp_gt_0))) * pull(prob1_df,samp)
```

I can convert the logical vector to numeric, and multiply the random sample by the result.
I can't convert the logical vector to a factor, and multiply the random sample by the result.
I can convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result.




## Problem 2


```{r prob2, echo = FALSE}

data("penguins", package = "palmerpenguins")

# get the names/values of the data
penguins

# get the size of the data frame
row = nrow(penguins)
col = ncol(penguins)

# calculate the mean flipper length
mean_flipper = mean(pull(penguins,flipper_length_mm), na.rm = TRUE)

# make a scatterplot of flipper length and bill length
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot_penguins.pdf", height = 4, width = 6)
```

This is a dataset about penguins. 

* It has 8 variables: `r ls(penguins)`.
  * The species variable contains `r unique(pull(penguins,species))`.
  * The sex variable contains `r unique(pull(penguins,sex))`.
  * The year variable contains `r unique(pull(penguins,year))`.
* This data set has `r row` rows and `r col` columns.
* The mean flipper length for penguins is `r round(mean_flipper,digits=2)` mm.
* The scatterplot shows that there is a potential positive linear relationship between bill length and flipper length. There are also significant differences of bill length and flipper length among species. 
  * Adelie generally have shorter flipper and bill.
  * Gentoo have longest flipper and bill
  * Chinstrap has similar bill length as Gentoo but shorter flipper.


